\section{Introduction, usage and implementation}% ===> this file was generated automatically by noweave --- better not edit it

This is by far the shortest include file in this collection.
What we provide here is a reasonable default set-up for make when working with 
Haskell.
In summary, we provide the following.
\nwfilename{haskell.mk.nw}\nwbegincode{1}\sublabel{NWRGmxa-2BVnEX-1}\nwmargintag{{\nwtagstyle{}\subpageref{NWRGmxa-2BVnEX-1}}}\moddef{\code{}haskell.mk\edoc{}~{\nwtagstyle{}\subpageref{NWRGmxa-2BVnEX-1}}}\endmoddef\nwstartdeflinemarkup\nwenddeflinemarkup
\LA{}default variables~{\nwtagstyle{}\subpageref{NWRGmxa-Iuse3-1}}\RA{}
\LA{}suffix rules for Haskell programs~{\nwtagstyle{}\subpageref{NWRGmxa-22vzcb-1}}\RA{}
\nwnotused{[[haskell.mk]]}\nwendcode{}\nwbegindocs{2}\nwdocspar

The Glasgow Haskell Compiler is functionally equivalent to the GNU C Compiler 
when compiling C programs.
It can also handle the linking step, which means that we can simply use GHC for
the linking step.
\nwenddocs{}\nwbegincode{3}\sublabel{NWRGmxa-Iuse3-1}\nwmargintag{{\nwtagstyle{}\subpageref{NWRGmxa-Iuse3-1}}}\moddef{default variables~{\nwtagstyle{}\subpageref{NWRGmxa-Iuse3-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NWRGmxa-2BVnEX-1}}\nwenddeflinemarkup
LD=   ghc
\nwused{\\{NWRGmxa-2BVnEX-1}}\nwendcode{}\nwbegindocs{4}And then we can provide the following suffix rule for compiling Haskell 
programs.
\nwenddocs{}\nwbegincode{5}\sublabel{NWRGmxa-22vzcb-1}\nwmargintag{{\nwtagstyle{}\subpageref{NWRGmxa-22vzcb-1}}}\moddef{suffix rules for Haskell programs~{\nwtagstyle{}\subpageref{NWRGmxa-22vzcb-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NWRGmxa-2BVnEX-1}}\nwenddeflinemarkup
.SUFFIXES: .hs .lhs
.hs.o .lhs.o:
  ghc $\{HSFLAGS\} -c $<
\nwused{\\{NWRGmxa-2BVnEX-1}}\nwendcode{}

\nwixlogsorted{c}{{\code{}haskell.mk\edoc{}}{NWRGmxa-2BVnEX-1}{\nwixd{NWRGmxa-2BVnEX-1}}}%
\nwixlogsorted{c}{{default variables}{NWRGmxa-Iuse3-1}{\nwixu{NWRGmxa-2BVnEX-1}\nwixd{NWRGmxa-Iuse3-1}}}%
\nwixlogsorted{c}{{suffix rules for Haskell programs}{NWRGmxa-22vzcb-1}{\nwixu{NWRGmxa-2BVnEX-1}\nwixd{NWRGmxa-22vzcb-1}}}%
\nwbegindocs{6}\nwdocspar

For weaving Haskell code, if the code is written using Haskell's native 
literate language, then that code is directly compilable as LaTeX code.
So we need not do any weaving for {\Tt{}.lhs\nwendquote} files.

\nwenddocs{}
