\section{Introduction and usage}% ===> this file was generated automatically by noweave --- better not edit it

The idea of this include file is to provide an easy way to package files 
together for publication.
It can be for packaging the source code of a document or package a script with 
automatic installation instructions.

The first thing we need for a package is a name.
This is controlled by the {\Tt{}PKG{\_}NAME\nwendquote} variable.
\nwfilename{pkg.mk.nw}\nwbegincode{1}\sublabel{NW3DMP9t-29jjeg-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW3DMP9t-29jjeg-1}}}\moddef{variables~{\nwtagstyle{}\subpageref{NW3DMP9t-29jjeg-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW3DMP9t-3JSaY2-1}}\nwprevnextdefs{\relax}{NW3DMP9t-29jjeg-2}\nwenddeflinemarkup
PKG_NAME?=          $\{PACKAGE\}
\nwalsodefined{\\{NW3DMP9t-29jjeg-2}\\{NW3DMP9t-29jjeg-3}\\{NW3DMP9t-29jjeg-4}\\{NW3DMP9t-29jjeg-5}\\{NW3DMP9t-29jjeg-6}\\{NW3DMP9t-29jjeg-7}\\{NW3DMP9t-29jjeg-8}\\{NW3DMP9t-29jjeg-9}}\nwused{\\{NW3DMP9t-3JSaY2-1}}\nwendcode{}\nwbegindocs{2}Its default value is set for backwards compatibility, so that makefiles using 
the old variable names will still work.
The package name will, by default, determine the name of the tarball that is 
generated.
\nwenddocs{}\nwbegincode{3}\sublabel{NW3DMP9t-29jjeg-2}\nwmargintag{{\nwtagstyle{}\subpageref{NW3DMP9t-29jjeg-2}}}\moddef{variables~{\nwtagstyle{}\subpageref{NW3DMP9t-29jjeg-1}}}\plusendmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW3DMP9t-3JSaY2-1}}\nwprevnextdefs{NW3DMP9t-29jjeg-1}{NW3DMP9t-29jjeg-3}\nwenddeflinemarkup
PKG_TARBALL?=       $\{PKG_NAME\}.tar.gz
\nwused{\\{NW3DMP9t-3JSaY2-1}}\nwendcode{}\nwbegindocs{4}\nwdocspar

The next thing we need is to control which files are included.
There are two types of files: files that should be installed and files that 
should not.
\nwenddocs{}\nwbegincode{5}\sublabel{NW3DMP9t-29jjeg-3}\nwmargintag{{\nwtagstyle{}\subpageref{NW3DMP9t-29jjeg-3}}}\moddef{variables~{\nwtagstyle{}\subpageref{NW3DMP9t-29jjeg-1}}}\plusendmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW3DMP9t-3JSaY2-1}}\nwprevnextdefs{NW3DMP9t-29jjeg-2}{NW3DMP9t-29jjeg-4}\nwenddeflinemarkup
PKG_INSTALL_FILES?= $\{INSTALL_FILES\}
PKG_TARBALL_FILES?= $\{PACKAGE_FILES\} $\{PKG_INSTALL_FILES\}
\nwused{\\{NW3DMP9t-3JSaY2-1}}\nwendcode{}\nwbegindocs{6}The tarball files will only be included in the tarball, but the install files
will be installed if the {\Tt{}install\nwendquote} target is made.
For example, a {\Tt{}Makefile\nwendquote} should be included (since it contains the 
installation target), but it should not be installed.
When the file lists include directories it might be interesting to ignore 
certain files, \eg version management.
This can be done with the following.
\nwenddocs{}\nwbegincode{7}\sublabel{NW3DMP9t-29jjeg-4}\nwmargintag{{\nwtagstyle{}\subpageref{NW3DMP9t-29jjeg-4}}}\moddef{variables~{\nwtagstyle{}\subpageref{NW3DMP9t-29jjeg-1}}}\plusendmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW3DMP9t-3JSaY2-1}}\nwprevnextdefs{NW3DMP9t-29jjeg-3}{NW3DMP9t-29jjeg-5}\nwenddeflinemarkup
IGNORE_FILES?=      \\(\\.svn\\|\\.git\\|CVS\\)
PKG_IGNORE?=        $\{IGNORE_FILES\}
\nwused{\\{NW3DMP9t-3JSaY2-1}}\nwendcode{}\nwbegindocs{8}\nwdocspar

The installation path is controlled by the following variables.
\nwenddocs{}\nwbegincode{9}\sublabel{NW3DMP9t-29jjeg-5}\nwmargintag{{\nwtagstyle{}\subpageref{NW3DMP9t-29jjeg-5}}}\moddef{variables~{\nwtagstyle{}\subpageref{NW3DMP9t-29jjeg-1}}}\plusendmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW3DMP9t-3JSaY2-1}}\nwprevnextdefs{NW3DMP9t-29jjeg-4}{NW3DMP9t-29jjeg-6}\nwenddeflinemarkup
PKG_PREFIX?=        $\{PREFIX\}
PKG_INSTALL_DIR?=   $\{INSTALLDIR\}
\nwused{\\{NW3DMP9t-3JSaY2-1}}\nwendcode{}\nwbegindocs{10}\nwdocspar

Sometimes different parts of a package must be installed to different places, 
\eg a script to {\Tt{}/usr/local/bin\nwendquote} and a manual page to 
{\Tt{}/usr/local/share/man\nwendquote}.
For this purpose, a package can be divided into several sub-packages.
By default we have one package called {\Tt{}main\nwendquote}.
\nwenddocs{}\nwbegincode{11}\sublabel{NW3DMP9t-29jjeg-6}\nwmargintag{{\nwtagstyle{}\subpageref{NW3DMP9t-29jjeg-6}}}\moddef{variables~{\nwtagstyle{}\subpageref{NW3DMP9t-29jjeg-1}}}\plusendmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW3DMP9t-3JSaY2-1}}\nwprevnextdefs{NW3DMP9t-29jjeg-5}{NW3DMP9t-29jjeg-7}\nwenddeflinemarkup
PKG_PACKAGES?=            main
\nwused{\\{NW3DMP9t-3JSaY2-1}}\nwendcode{}\nwbegindocs{12}For each such package we can set a specialized version of the variables we 
discussed above.
By default, they will inherit the global values set above.
\nwenddocs{}\nwbegincode{13}\sublabel{NW3DMP9t-29jjeg-7}\nwmargintag{{\nwtagstyle{}\subpageref{NW3DMP9t-29jjeg-7}}}\moddef{variables~{\nwtagstyle{}\subpageref{NW3DMP9t-29jjeg-1}}}\plusendmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW3DMP9t-3JSaY2-1}}\nwprevnextdefs{NW3DMP9t-29jjeg-6}{NW3DMP9t-29jjeg-8}\nwenddeflinemarkup
define variables
PKG_NAME-$(1)?=           $\{PKG_NAME\}
PKG_INSTALL_FILES-$(1)?=  $\{PKG_INSTALL_FILES\}
PKG_PREFIX-$(1)?=         $\{PKG_PREFIX\}
PKG_INSTALL_DIR-$(1)?=    $\{PKG_INSTALL_DIR\}

PKG_TARBALL-$(1)?=        $\{PKG_NAME-$(1)\}.tar.gz
PKG_TARBALL_FILES-$(1)?=  $\{PKG_TARBALL_FILES\}
PKG_IGNORE-$(1)?=         $\{PKG_IGNORE\}
endef
\nwused{\\{NW3DMP9t-3JSaY2-1}}\nwendcode{}\nwbegindocs{14}Then we use this as a function to set the variables for each sub-package.
\nwenddocs{}\nwbegincode{15}\sublabel{NW3DMP9t-29jjeg-8}\nwmargintag{{\nwtagstyle{}\subpageref{NW3DMP9t-29jjeg-8}}}\moddef{variables~{\nwtagstyle{}\subpageref{NW3DMP9t-29jjeg-1}}}\plusendmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW3DMP9t-3JSaY2-1}}\nwprevnextdefs{NW3DMP9t-29jjeg-7}{NW3DMP9t-29jjeg-9}\nwenddeflinemarkup
$(foreach pkg,$\{PKG_PACKAGES\},$(eval $(call variables,$\{pkg\})))
\nwused{\\{NW3DMP9t-3JSaY2-1}}\nwendcode{}\nwbegindocs{16}\nwdocspar

\subsection{Portability}

For portability, this include file requires the following programs to be 
available.
\nwenddocs{}\nwbegincode{17}\sublabel{NW3DMP9t-29jjeg-9}\nwmargintag{{\nwtagstyle{}\subpageref{NW3DMP9t-29jjeg-9}}}\moddef{variables~{\nwtagstyle{}\subpageref{NW3DMP9t-29jjeg-1}}}\plusendmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW3DMP9t-3JSaY2-1}}\nwprevnextdefs{NW3DMP9t-29jjeg-8}{\relax}\nwenddeflinemarkup
ifneq ($\{MAKE\},gmake)
INSTALL?=     $\{SUDO\} install -Dp
else
INSTALL?=     $\{SUDO\} install -CSp
endif
\nwused{\\{NW3DMP9t-3JSaY2-1}}\nwendcode{}\nwbegindocs{18}\nwdocspar


\section{Implementation}

This is an include file, so we will use a C-style header construction to 
prevent it from being included more than once.
Then the overview of the structure is as follows.
\nwenddocs{}\nwbegincode{19}\sublabel{NW3DMP9t-3JSaY2-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW3DMP9t-3JSaY2-1}}}\moddef{\code{}pkg.mk\edoc{}~{\nwtagstyle{}\subpageref{NW3DMP9t-3JSaY2-1}}}\endmoddef\nwstartdeflinemarkup\nwenddeflinemarkup
ifndef PACKAGE_MK
PACKAGE_MK=true

INCLUDE_MAKEFILES?=.
include $\{INCLUDE_MAKEFILES\}/portability.mk

\LA{}variables~{\nwtagstyle{}\subpageref{NW3DMP9t-29jjeg-1}}\RA{}
\LA{}an all-like target~{\nwtagstyle{}\subpageref{NW3DMP9t-2MPZQk-1}}\RA{}
\LA{}targets for packaging~{\nwtagstyle{}\subpageref{NW3DMP9t-19q7UA-1}}\RA{}
\LA{}targets for cleaning~{\nwtagstyle{}\subpageref{NW3DMP9t-LrkAl-1}}\RA{}
\LA{}targets for installation~{\nwtagstyle{}\subpageref{NW3DMP9t-186wP-1}}\RA{}

endif
\nwnotused{[[pkg.mk]]}\nwendcode{}\nwbegindocs{20}\nwdocspar

We want to have an all-like target, we call it {\Tt{}package\nwendquote}.
The {\Tt{}package\nwendquote} target should, of course, have all tarballs as prerequisites.
The reason for not using {\Tt{}all\nwendquote} is that we leave the {\Tt{}all\nwendquote} target for the 
user, with its prerequisites defined in the main makefile.
\nwenddocs{}\nwbegincode{21}\sublabel{NW3DMP9t-2MPZQk-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW3DMP9t-2MPZQk-1}}}\moddef{an all-like target~{\nwtagstyle{}\subpageref{NW3DMP9t-2MPZQk-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW3DMP9t-3JSaY2-1}}\nwenddeflinemarkup
.PHONY: package
package: $(foreach pkg,$\{PKG_PACKAGES\},$\{PKG_TARBALL-$\{pkg\}\})
\nwused{\\{NW3DMP9t-3JSaY2-1}}\nwendcode{}\nwbegindocs{22}\nwdocspar

\subsection{Packaging}

The packaging step shall take the files specified and create a tarball 
containing them.
What we will do is to create a target for the tarball.
We will do this by using the archive functionality of make(1) and the 
compression functionality we added in \cref{portability:Archives}.
\nwenddocs{}\nwbegincode{23}\sublabel{NW3DMP9t-19q7UA-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW3DMP9t-19q7UA-1}}}\moddef{targets for packaging~{\nwtagstyle{}\subpageref{NW3DMP9t-19q7UA-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW3DMP9t-3JSaY2-1}}\nwenddeflinemarkup
define tarball
$(foreach f,$\{PKG_TARBALL_FILES-$(1)\},\\
  $(eval $\{PKG_TARBALL-$(1)\}($\{f\}): $\{f\}))
$\{PKG_TARBALL-$(1)\}: $\{PKG_TARBALL-$(1)\}($\{PKG_TARBALL_FILES-$(1)\})
endef
$(foreach pkg,$\{PKG_PACKAGES\},$(eval $(call tarball,$\{pkg\})))
\nwused{\\{NW3DMP9t-3JSaY2-1}}\nwendcode{}\nwbegindocs{24}\nwdocspar

\subsection{Cleaning}

The kind of cleaning we are interested in is to remove the tarballs that we 
generate.
The other files, install and tarball files, should be cleaned using other 
cleaning targets --- if they need cleaning at all.

The technique we use is to provide a {\Tt{}clean-package\nwendquote} target which we add as 
a prerequisite to the general target {\Tt{}clean\nwendquote}.
This way the user can have a recipe for {\Tt{}clean\nwendquote} in the main makefile without 
us interfering.
\nwenddocs{}\nwbegincode{25}\sublabel{NW3DMP9t-LrkAl-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW3DMP9t-LrkAl-1}}}\moddef{targets for cleaning~{\nwtagstyle{}\subpageref{NW3DMP9t-LrkAl-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW3DMP9t-3JSaY2-1}}\nwprevnextdefs{\relax}{NW3DMP9t-LrkAl-2}\nwenddeflinemarkup
.PHONY: clean clean-package
clean: clean-package
\nwalsodefined{\\{NW3DMP9t-LrkAl-2}}\nwused{\\{NW3DMP9t-3JSaY2-1}}\nwendcode{}\nwbegindocs{26}\nwdocspar

We now create a cleaning target for each sub-package and add those as 
prerequisites for the {\Tt{}clean-package\nwendquote} target.
The recipe is to remove the tarball of that particular sub-package.
\nwenddocs{}\nwbegincode{27}\sublabel{NW3DMP9t-LrkAl-2}\nwmargintag{{\nwtagstyle{}\subpageref{NW3DMP9t-LrkAl-2}}}\moddef{targets for cleaning~{\nwtagstyle{}\subpageref{NW3DMP9t-LrkAl-1}}}\plusendmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW3DMP9t-3JSaY2-1}}\nwprevnextdefs{NW3DMP9t-LrkAl-1}{\relax}\nwenddeflinemarkup
define clean-package
.PHONY: clean-package-$(1)
clean-package: clean-package-$(1)
clean-package-$(1):
  $\{RM\} $\{PKG_TARBALL-$(1)\}
endef
$(foreach pkg,$\{PKG_PACKAGES\},$(eval $(call clean-package,$\{pkg\})))
\nwused{\\{NW3DMP9t-3JSaY2-1}}\nwendcode{}\nwbegindocs{28}\nwdocspar

\subsection{Installation}

The {\Tt{}install\nwendquote} target will install the files that are configured to be 
installed where they are configured to be installed.
The installation process proceeds in the following steps.
\nwenddocs{}\nwbegincode{29}\sublabel{NW3DMP9t-4WrEJg-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW3DMP9t-4WrEJg-1}}}\moddef{installation process~{\nwtagstyle{}\subpageref{NW3DMP9t-4WrEJg-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW3DMP9t-186wP-1}}\nwenddeflinemarkup
.PHONY: pre-install do-install post-install
post-install: do-install
do-install:   pre-install
pre-install:  $\{PKG_INSTALL_FILES\}
\nwused{\\{NW3DMP9t-186wP-1}}\nwendcode{}\nwbegindocs{30}This will ensure that the targets' recipes are run in the desired order 
(since the prerequisites' recipes are run first, if needed).
This means that the files to be installed are made before {\Tt{}pre-install\nwendquote} is 
run.
To start the process with the {\Tt{}install\nwendquote} target, we add the following.
\nwenddocs{}\nwbegincode{31}\sublabel{NW3DMP9t-186wP-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW3DMP9t-186wP-1}}}\moddef{targets for installation~{\nwtagstyle{}\subpageref{NW3DMP9t-186wP-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW3DMP9t-3JSaY2-1}}\nwprevnextdefs{\relax}{NW3DMP9t-186wP-2}\nwenddeflinemarkup
.PHONY: install
install: post-install
\LA{}installation process~{\nwtagstyle{}\subpageref{NW3DMP9t-4WrEJg-1}}\RA{}
\nwalsodefined{\\{NW3DMP9t-186wP-2}}\nwused{\\{NW3DMP9t-3JSaY2-1}}\nwendcode{}\nwbegindocs{32}\nwdocspar

Now we need to provide package dependent versions of these targets.
We achieve this by simply adding the package dependent versions as 
prerequisites for the general targets, and in the same order as we did for the 
general targets.
\nwenddocs{}\nwbegincode{33}\sublabel{NW3DMP9t-186wP-2}\nwmargintag{{\nwtagstyle{}\subpageref{NW3DMP9t-186wP-2}}}\moddef{targets for installation~{\nwtagstyle{}\subpageref{NW3DMP9t-186wP-1}}}\plusendmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW3DMP9t-3JSaY2-1}}\nwprevnextdefs{NW3DMP9t-186wP-1}{\relax}\nwenddeflinemarkup
define post-install
.PHONY: post-install-$(1)
post-install: post-install-$(1)
post-install-$(1): do-install-$(1)
endef
$(foreach pkg,$\{PKG_PACKAGES\},$(eval $(call post-install,$\{pkg\})))

define do-install
.PHONY: do-install-$(1)
do-install: do-install-$(1)
do-install-$(1): pre-install-$(1)
  \LA{}default do-install recipe~{\nwtagstyle{}\subpageref{NW3DMP9t-2CDbER-1}}\RA{}
endef
$(foreach pkg,$\{PKG_PACKAGES\},$(eval $(call do-install,$\{pkg\})))

define pre-install
.PHONY: pre-install-$(1)
pre-install: pre-install-$(1)
pre-install-$(1): $\{PKG_INSTALL_FILES-$(1)\}
endef
$(foreach pkg,$\{PKG_PACKAGES\},$(eval $(call pre-install,$\{pkg\})))
\nwused{\\{NW3DMP9t-3JSaY2-1}}\nwendcode{}\nwbegindocs{34}\nwdocspar

Finally, we need a default recipe for the {\Tt{}do-install\nwendquote} target, otherwise the 
user would have to write one every time --- and that would counter the purpose 
of this include file.
The procedure is straight-forward.
We first create the target directory, with a possible prefix.
Then, for every non-directory, we install using the {\Tt{}install\nwendquote} command.
\nwenddocs{}\nwbegincode{35}\sublabel{NW3DMP9t-2CDbER-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW3DMP9t-2CDbER-1}}}\moddef{default do-install recipe~{\nwtagstyle{}\subpageref{NW3DMP9t-2CDbER-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW3DMP9t-186wP-2}}\nwenddeflinemarkup
for f in $\{PKG_INSTALL_FILES-$(1)\}; do \\
  [ -d "$$$$f" ] || $\{INSTALL\} -t $\{PKG_PREFIX-$(1)\}$\{PKG_INSTALL_DIR-$(1)\}/ "$$$$f"; \\
done
\nwused{\\{NW3DMP9t-186wP-2}}\nwendcode{}

\nwixlogsorted{c}{{\code{}pkg.mk\edoc{}}{NW3DMP9t-3JSaY2-1}{\nwixd{NW3DMP9t-3JSaY2-1}}}%
\nwixlogsorted{c}{{an all-like target}{NW3DMP9t-2MPZQk-1}{\nwixu{NW3DMP9t-3JSaY2-1}\nwixd{NW3DMP9t-2MPZQk-1}}}%
\nwixlogsorted{c}{{default do-install recipe}{NW3DMP9t-2CDbER-1}{\nwixu{NW3DMP9t-186wP-2}\nwixd{NW3DMP9t-2CDbER-1}}}%
\nwixlogsorted{c}{{installation process}{NW3DMP9t-4WrEJg-1}{\nwixd{NW3DMP9t-4WrEJg-1}\nwixu{NW3DMP9t-186wP-1}}}%
\nwixlogsorted{c}{{targets for cleaning}{NW3DMP9t-LrkAl-1}{\nwixu{NW3DMP9t-3JSaY2-1}\nwixd{NW3DMP9t-LrkAl-1}\nwixd{NW3DMP9t-LrkAl-2}}}%
\nwixlogsorted{c}{{targets for installation}{NW3DMP9t-186wP-1}{\nwixu{NW3DMP9t-3JSaY2-1}\nwixd{NW3DMP9t-186wP-1}\nwixd{NW3DMP9t-186wP-2}}}%
\nwixlogsorted{c}{{targets for packaging}{NW3DMP9t-19q7UA-1}{\nwixu{NW3DMP9t-3JSaY2-1}\nwixd{NW3DMP9t-19q7UA-1}}}%
\nwixlogsorted{c}{{variables}{NW3DMP9t-29jjeg-1}{\nwixd{NW3DMP9t-29jjeg-1}\nwixd{NW3DMP9t-29jjeg-2}\nwixd{NW3DMP9t-29jjeg-3}\nwixd{NW3DMP9t-29jjeg-4}\nwixd{NW3DMP9t-29jjeg-5}\nwixd{NW3DMP9t-29jjeg-6}\nwixd{NW3DMP9t-29jjeg-7}\nwixd{NW3DMP9t-29jjeg-8}\nwixd{NW3DMP9t-29jjeg-9}\nwixu{NW3DMP9t-3JSaY2-1}}}%
\nwbegindocs{36}\nwdocspar
\nwenddocs{}
